Map

### 2019-06-13 r/map_exp.Rmd
updating map/shapefiles

```{r}
library(tidyverse)
library(here)
library(sf)
library(ggmap)

site_data <- read.csv(here("data","site_coord.csv"))

# shape files for islands
atg <- read_sf("bes_adm1")

atg.shp <- system.file(here("data", "map", "atg", "atg.shp", package="sf"))
atg <- st_read(atg.shp)
bes.shp <- system.file("bes_adm1", package="sf")
bes <- st_read("bes.shp")

download.file("http://github.com/mgimond/Spatial/raw/master/Data/Income_schooling.zip", 
              destfile = "Income_schooling.zip" , mode='wb')
unzip("Income_schooling.zip", exdir = ".")
file.remove("Income_schooling.zip")
s.sf <- st_read("Income_schooling.shp")

download.file("http://github.com/mgimond/Spatial/raw/master/Data/Income_schooling.zip", 
              destfile = "Income_schooling.zip")
```

```{r}
atg_map <- read_sf(atg)
atg_map <- st_read("data/map/atg/atg.shp")
```

```{r}
map.world <- map_data("world", region = "Bonaire")
ggplot(map.world, aes(x=long, y=lat)) +
  geom_polygon(colour = "white")

islands <- c("Antigua","Barbuda","Bonaire")
ll.islands <- geocode(islands)
islands.x <- ll.islands$lon
islands.y <- ll.islands$lat

ggplot() +
  theme_bw() +
  geom_polygon(data = map.world, aes(x = long, y = lat))+
  coord_equal(xlim = c(-100, -60),ylim = c(27,10)) +
  geom_point(aes(x=islands.x, y=islands.y), color="#f24db3", size=5) +
  labs(x = "", y="",title = "")
```

```{r}
m_antigua <- get_map(location="Antigua", source="stamen", maptype="toner-lite", bbox = c(left = 110, bottom = -40, right = 160, top = -10), zoom=11)
ggmap(m_antigua)

m_carib <- get_map(location="Caribbean")
ggmap(m_carib)

antigua <- map_data("usa")
```

```{r}
ggplot(data = world) +
    geom_sf() +
    coord_sf(xlim = c(-102.15, -74.12), ylim = c(7.65, 33.97), expand = FALSE)
```

# Build base map, which we'll use for rest of maps
base_map <- ggplot()+ 
  geom_sf(data=world_land %>%
            mutate(Country = ifelse(ISO3 %in% c("BRA","PHL","IDN"),"Target","Other")), 
          color = NA, aes(fill=Country)) +
  scale_fill_manual(values=c("grey85","grey60")) +
  scale_color_manual(values = pal,name = "Site Type") +
  scale_shape_manual(values = shape_pal,name = "Site Type") +
  geom_sf(data = site_coords, aes(shape=site_type),color = "black",size=2.5, show.legend = FALSE) +
  geom_sf(data = site_coords,aes(color=site_type,shape=site_type), show.legend = "point",size=2) +
  guides(fill=FALSE)+
  theme_bw() +
  theme(plot.title = element_text(color="black",hjust=0,vjust=1, size=rel(1)),
        panel.border = element_rect(color = 'black', fill = NA,size=1),
        panel.grid.major = element_line(colour = "white"), 
        legend.text = element_text(color = "black", size = rel(2)),
        legend.title = element_text(color = "black", size = rel(2)),
        legend.title.align = 1,
        legend.background = element_rect(fill="white"),
        legend.position = "right",
        legend.direction="vertical",
        legend.text.align = 0,
        axis.text = element_text(color = "black", size = rel(1)),
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + 
  guides(colour = guide_legend(override.aes = list(size=4)))

world_map <- base_map +
  geom_sf(data = philippines_bbox%>%
            st_as_sfc(),fill=NA) +
  geom_sf(data = indonesia_bbox%>%
            st_as_sfc(),fill=NA) +
  geom_sf(data = brazil_bbox%>%
            st_as_sfc(),fill=NA) +
  guides(color = FALSE,shape=FALSE)+
  xlim(c(world_bbox[1], world_bbox[3])) +
  ylim(c(world_bbox[2], world_bbox[4]))

brazil_map <- base_map +
  xlim(c(brazil_bbox[1], brazil_bbox[3])) +
  ylim(c(brazil_bbox[2], brazil_bbox[4])) +
  guides(color = FALSE,shape=FALSE)

indonesia_map <- base_map +
  xlim(c(indonesia_bbox[1], indonesia_bbox[3])) +
  ylim(c(indonesia_bbox[2], indonesia_bbox[4])) +
  guides(color = FALSE,shape=FALSE)

philippines_map <- base_map +
  xlim(c(philippines_bbox[1], philippines_bbox[3])) +
  ylim(c(philippines_bbox[2], philippines_bbox[4])) +
  guides(color = FALSE,shape=FALSE)

# Put all maps together
combined_map <- plot_grid(plot_grid(world_map,labels = "A"),
                          plot_grid(brazil_map, philippines_map, labels = c("B", "C"), rel_widths = c(0.65,0.35)),
                          plot_grid(indonesia_map, get_legend(base_map), labels = c("D", ""), rel_widths = c(0.65,0.35)),
                          ncol=1,
                          rel_heights = c(1,0.8,0.5))

ggsave(paste0("paper_package/figures/figure_1_map.png"),combined_map,width = 7.5,height=7.5,device="png",dpi=300)

>>>>

```{r}
library(tidyverse)
library(here)
library(sf)
library(ggmap)
# library(ggspatial)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggrepel)

# site coordinates
site_data <- read.csv(here("data","map","site_coord.csv"))

# shapefiles for islands filtered from BES and ATG boundaries
bonaire <- st_read(here("data","map","BES_adm1.shp")) %>% 
  filter(NAME_1 == "Bonaire") %>%
  st_union() %>%
  st_sf() %>%
  mutate(island = "Bonaire")

atg <- st_read(here("data","map","ATG_adm1_gadm.shp")) 
antigua <- atg %>%
  filter(!NAME_1 == c("Barbuda","Redonda")) %>%
  st_union() %>%
  st_sf() %>%
  mutate(island = "Antigua")
barbuda <- atg %>% 
  filter(NAME_1 == "Barbuda") %>%
  st_union() %>%
  st_sf() %>%
  mutate(island = "Barbuda")

islands <- rbind(antigua, barbuda, bonaire) %>%
  mutate(lon=map_dbl(geometry, ~st_centroid(.x)[[1]]), 
         lat=map_dbl(geometry, ~st_centroid(.x)[[2]]))

# google API (not sure if I can register this permanently?)
register_google(key = "AIzaSyDvckfjy2riROUUuL9oDg7HBXRBd39X82A")
```

### Regional map

```{r}
world <- ne_countries(scale = "large", returnclass = "sf")
ggplot() +
  geom_sf(data = world, fill = "gray80", col = "gray80", size = .25) +
  geom_sf(data = islands, fill = "gray20", col = "gray20", size = .25) +
  #geom_text_repel(data = islands %>% filter(island %in% c("Antigua","Barbuda")), aes(x = lon, y = lat, label = island), nudge_x = 6, segment.size = .2) +
  #geom_text_repel(data = islands %>% filter(island == "Bonaire"), aes(x = lon, y = lat, label = island), nudge_x = -2, nudge_y = 2, segment.size = .2) +
  #annotate(geom = "text", x = -86.5, y = 26, label = "Gulf of Mexico", fontface = "italic", color = "grey80", size = 3) +
  annotate(geom = "text", x = -65, y = 29, label = "Atlantic Ocean", fontface = "italic", color = "grey80", size = 4) +
  annotate(geom = "text", x = -72.5, y = 15, label = "Caribbean Sea", fontface = "italic", color = "grey80", size = 4) +
  coord_sf(xlim = c(-86, -58), ylim = c(10, 33), expand = FALSE) +
  labs(x = "", y = "") +
  theme_bw()
ggsave(here("figs/map_region.png"))
```

Alternate (geocoding) option
```{r}
#world <- map_data("world") # df
ll.islands <- geocode(c("Antigua","Barbuda","Bonaire"))
islands.x <- ll.islands$lon
islands.y <- ll.islands$lat

ggplot() +
  theme_bw() +
  geom_sf(data = world, fill = "gray80", col = "gray80") +
  annotation_scale(location = "tr", width_hint = 0.25) +
  coord_sf(xlim = c(-90, -58), ylim = c(10, 33)) +
  geom_point(aes(x = islands.x, y = islands.y), color = "#f24db3", size = 5, shape = 1) +
  labs(x = "", y = "",title = "")

```

### Island-level details

```{r}
sites_anu <- site_data %>% filter(island == "Antigua")
ggplot() +
  geom_sf(data = antigua, fill = "slategray4", color = "slategray4") +
  geom_point(data = sites_anu, aes(x = lon, y = lat), color = "gray20", size = 2) +
  geom_text_repel(data = sites_anu,
                  aes(x = lon, y = lat, label = site),
                  segment.size = .2,
                  direction = "y",
                  box.padding = .75,
                  nudge_x = .18, nudge_y = .08,
                  size = 5) +
  coord_sf(xlim = c(-61.92, -61.52), ylim = c(16.98, 17.18)) +
  annotation_scale(location = "bl", width_hint = 0.25) +
  theme_bw() +
  theme(axis.text = element_blank(), axis.ticks = element_blank(), axis.title = element_blank(), panel.grid.major = element_line(color = "transparent"))

ggsave(here("figs/map_anu.png"))
```

```{r}
sites_brb <- site_data %>% filter(island == "Barbuda")
ggplot() +
  geom_sf(data = barbuda, fill = "slategray4", color = "slategray4") +
  geom_point(data = sites_brb, aes(x = lon, y = lat), color = "gray20", size = 2) +
  geom_text_repel(data = sites_brb,
                  aes(x = lon, y = lat, label = site),
                  segment.size = .2,
                  direction = "y",
                  box.padding = .75,
                  nudge_x = .18, nudge_y = .12,
                  size = 5) +
  coord_sf(xlim = c(-61.9, -61.44), ylim = c(17.51, 17.74)) +
  annotation_scale(location = "bl", width_hint = 0.25) +
  theme_bw() +
  theme(axis.text = element_blank(), axis.ticks = element_blank(), axis.title = element_blank(), panel.grid.major = element_line(color = "transparent"))

ggsave(here("figs/map_brb.png"))
```

```{r}
sites_bon <- site_data %>% filter(island == "Bonaire")
ggplot() +
  geom_sf(data = bonaire, fill = "slategray4", color = "slategray4") +
  geom_point(data = sites_bon, aes(x = lon, y = lat), color = "gray20", size = 2) +
  geom_text_repel(data = sites_bon,
                  aes(x = lon, y = lat, label = site),
                  segment.size = .2,
                  direction = "y",
                  box.padding = .75,
                  nudge_x = .22, nudge_y = .02,
                  size = 5) +
  coord_sf(xlim = c(-68.45, -67.85), ylim = c(12.02, 12.32)) +
  annotation_scale(location = "bl", width_hint = 0.25) +
  theme_bw() +
  theme(axis.text = element_blank(), axis.ticks = element_blank(), axis.title = element_blank(), panel.grid.major = element_line(color = "transparent"))

ggsave(here("figs/map_bon.png"))
```
